---
title: "Willamette Falls fish passage time series summary"
author: "Joseph Kilgallen"
date: "3/8/2022"
output: 
  html_document:
    theme: spacelab
    highlight: tango
    code_folding: hide
---

**Your .Rmd must be customized as follows:**

-With a non-default theme (for example using bootstrap themes, with a custom theme, or with a theme from another package)

- With a separate tab for each of the three sections below the Overview (see this section on tabs in RMarkdown: The Definitive Guide by Yihui Xie, J. J. Allaire, and Garrett Grolemund)

- The document should be cohesive in presentation and communication (e.g. all graphs should use the same theming, consistent color schemes, etc.)

```{r setup, class.source = 'fold-show', include= TRUE, warning = FALSE, message= FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(prettydoc)
library(tidyverse)
library(here)
library(broom)
library(sf)
library(tmap)
library(gstat)
library(stars)
```

## Overview {.tabset .tabset-pills}

**An engaging image**
(with caption, incl. photo credit) that is relevant to the dataset

**Report Summary** 
A brief summary (3 - 4 sentences) of the dataset, and what is included in this report

**A map of the fish ladder location**
(you can make this in R on your own, or include an existing map appropriately licensed, with attribution)

**Data Citation**
A professionally formatted data citation

```{r}
## reading in the data and cleaning up
will <- read_csv(here::here("data", "willamette.csv")) %>% 
  janitor::clean_names()
```

### Original time series data
A finalized, static graph of adult passage for coho, jack coho, and steelhead salmon (you decide if these all occupy the same panel, or if they are in separate panels). Add a figure caption. Replace NA values with zero. 
```{r}
## subset the data for this chart

## want data just for coho, jack coho and salmon
will_static <- will %>% 
  select(c("coho", "jack_coho", "steelhead", "date")) %>% 
  mutate()
  
```


**Takeaways**
2 - 3 bullet points summarizing major patterns / notable trends in the salmon passage time series data


### Seasonplots
Tab 2: 
A finalized seasonplot for each species (coho, jack coho, steelhead) in its own panel. You can either facet_wrap/facet_grid, or use patchwork or cowplot, to make the figure. Add a caption.
Add 2 - 3 bullet points summarizing the major trends you see in the seasonplots.


### Annual counts by species
A finalized figure of annual totals for fish passage, for each of the 3 species (coho, jack coho, steelhead). 

You decide if this is in a single panel, or multiple panels. Add a figure caption. 
Add 2 - 3 bullet points summarizing major trends you see in the annual totals by species from 2000 - 2010.
